\cvsection{Relevant Experience}

\begin{cventries}

  \cventry
    {Digital UX Designer - Co-op Student}
    {H\&R Block Canada}
    {Calgary, Canada}
    {May 2016 - Present}
    {
      \begin{cvitems}
        \item {Design tax forms, flows, and features by gathering requirements and dissecting competitor flows using Moqups and Axure.}
        \item {Plan usability studies, analyze participants in thinking aloud tests, and compile reports with recommendations.}
        \item {Implement front-end changes using HTML, CSS, and Angular.js, provide code reviews, and perform quality assurance.}
        \item {Analyze feedback surveys \& NPS comments to present trends in Tableau, and provide usability improvements.}
        \item {Created guides to maintain code consistency and improve on-boarding for the UX team using Confluence and Axure.}
        \item {Collaborate with multiple teams to discuss user needs, provide feedback, and improve designs. Contributions helped significantly increase user base, NPS scores, and NPS comments for the 2016 tax software.}
      \end{cvitems}
    }

  \cventry
    {Developer Intern}
    {Critical Mass}
    {Calgary, Canada}
    {May 2015 - August 2015}
    {
      \begin{cvitems}
        \item {Collaborated with an interdisciplinary team to create a strategic plan, creative design, social campaign, technical document, and a prototype in HTML5, Less, and Javascript for a mobile application where users rate accessible businesses.}
        \item {Designed and developed mobile capabilities, a blog, and event calendar in an existing Wordpress site using HTML, CSS, and Javascript; this included a detailed end user document discussing how to use the site.}
        \item {Developed design layouts into responsive prototypes using HTML, Sass, Middleman, Adobe CQ5, and Grails.}
        %\item {Implemented changes for the Nissan website by tracking changes with JIRA and using Adobe CQ5, Grails, HTML, and CSS.}
      \end{cvitems}
    }

  \cventry
    {Undergraduate Research Assistant}
    {Innovations in Visualization Laboratory, Interactions Lab}
    {Calgary, Canada}
    {May 2013 - April 2016}
    {
      \begin{cvitems}
        \item {Sketched and prototyped a visualization in Processing (Java) representing products as fingerprints.}
        \item {Designed and presented a workshop paper and poster at an IEEE VIS workshop and Canadian Women in Computing conference.}
        \item {Analyzed qualitative data using open coding practices and contributed to a paper on how non-scientific disciplines utilize Large, High-Resolution Displays, presented at the Interactive Tabletops \& Surfaces conference.}
      \end{cvitems}
    }

%  \cventry
%    {Summer Student}
%    {Nureva}
%    {Calgary, Canada}
%    {May 2014 - August 2014}
%    {
%      \begin{cvitems}
%        \item {Led development for a C\# and WPF client application and integrated the University of Calgary's SoD (Society of Devices) framework, which allows multiple devices to communicate together and utilize spatial awareness.}
%        \item {Developed, debugged, and implemented demonstrations for the client application.}
%        \item {Increased the company's brand through blog posts and presented research to guide developers and project managers about different strategy processes and mobile application types.}
%      \end{cvitems}  
%    }
 \end{cventries}
